---
title: "Introduction"
author: "Will Lowe"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
library(knitr)

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
knit_hooks$set(wrapper = function(before, options, envir) {
  if (before) {
    sprintf('    ```{r %s}\n', options$params.src)
  } else '    ```\n'
})

# Ascii tree from Jenny Bryan (adjusted to use a unicode arrow)
# https://gist.github.com/jennybc/2bf1dbe6eb1f261dfe60
twee <- function(path = getwd(), level = Inf) {
  fad <- list.files(path = path, recursive = TRUE, 
                    no.. = TRUE, include.dirs = TRUE)
  fad_split_up <- strsplit(fad, "/")
  too_deep <- lapply(fad_split_up, length) > level
  fad_split_up[too_deep] <- NULL
  jfun <- function(x) {
    n <- length(x)
    if (n > 1)
      x[n - 1] <- "\U21b3 "
    if (n > 2)
      x[1:(n - 2)] <- "   "
    x <- if (n == 1) c("- ", x) else c("  ", x)
    x
  }
  fad_subbed_out <- lapply(fad_split_up, jfun)
  cat(unlist(lapply(fad_subbed_out, paste, collapse = "")), sep = "\n")
}
```

## Problem sets

The `qss.student` package contains the questions and data sets from the 
problem sets in

> K. Imai (2016) 'Quantitative Social Science: An Introduction', Princeton
> University Press 

plus a few extra problem sets not in the book.

## Unpacking a problem set

Imagine you are assigned a problem set from the book called `bias-in-turnout`.
To complete the problem set make sure you have the package loaded
```{r, eval = TRUE}
library(qss.student)
```
and unpack the problem set into your current working directory
```{r}
get_pset("bias-in-turnout")
```
The current working directory should now look like this:

    - bias-in-turnout
      ↳ bias-in-turnout.pdf
      ↳ bias-in-turnout.Rmd
      ↳ bias-in-turnout.tex
      ↳ data
         ↳ turnout.csv

that is, a folder called `bias-in-turnout` and inside it 

* `bias-in-turnout.pdf`: a short description of the problem and the data
* `bias-in-turnout.Rmd`: the source file for the problem set
* `data` another folder containing all the data needed to complete the problem 
   set
* `data/turnout.csv`: the data set

As `get_pset` messages suggest, let's make the problem set folder our working
directory
```{r}
setwd("bias-in-turnout")
```
and open up the Rmd file so we can start filling in the answers to each question
```{r}
file.edit("bias-in-turnout.Rmd")
```
If you're in RStudio the file should now be editor tab.  

## Answering the questions

Each question has a header that looks like 

    ## Question 1

To provide an answer to this question, move your cursor to just above the 
line that says `## Question 2` and start answering the question.  When you 
need to compute something in R, start a 'code block'.  Here's a 
bit of text you might write followed by a code block that
loads the data set we need and counts the number of observations in it:

    We load the data set and count the rows
    ```{r}`r ''`
    turnout <- read.csv("data/turnout.csv")
    nrow(turnout)
    ```

You can have as much text and as many code blocks as you like.  (The variables
you make in one code block are still there in the next one.)

You can either type the beginning and end lines of the code block 
or you can press the green Insert button in the Editor 
pane's button menu, choose
'R', and have it done for you.  Just don't forget to put the code inside the 
backticks and don't nest code blocks inside one another or everything will
get confused.

## Compiling the problem set

Yo can see what your answers look like at any point by pressing the 'Knit' 
button.  This will try to run all your code, read all your answers and knit the 
two together into a document.  What *kind* of a document is controllable from 
that button.  If you chose 'Knit to HTML' (the default) your document will be 
called  'bias-in-turnout.html'.  If you chose 'Knit to PDF' or 'Knit to Word' 
it will have a different suffix.

You can compile whenever you like. Somee people like to work in the Rmd file
all the time and Knit intermittently to check their code works.  Others, 
particularly when starting off, prefer to do their thinking and coding in 
a different document and then paste their working code and answers into 
the Rmd file at the last minute.  Whatever works for you.

## Getting into (and out of) trouble

Sometimes you might feel it's best to start again with a fresh copy of 
the problem set.  However, if you 
```{r}
get_pset("bias-in-turnout")
```
then you'll get a new problem set inside the one you're abandoning.  This
makes things quite confusing.  It's better to go to top level of your files
and grab a new copy, calling it something else.  You can move your
working directory up a level with
```{r}
setwd("..")
```
In the language of file paths `..` means go up into the parent folder i.e. up
one level.  (In case you're curious, `.` indicates the *current folder*, and if
you wanted to go up *two* levels then `../..` would be what you wanted) 

Now you're back to where you unpacked `bias-in-turnout`.  To grab a fresh
copy with another name:
```{r}
get_pset("bias-in-turnout", newname = "bias-in-turnout-the-sequel")
```
(You may have a better idea for a name.) Now you can do it all again,
only better.

## All the other problem sets

If you're curious about the other problem sets you can get a list of their 
names with
```{r, eval = TRUE}
list_psets()
```
and you can take a peek at one of them (`constitutions`) without unpacking any 
files using
```{r}
preview_pset("constitutions")
```



